---
title: "Meta-Analysis Assignment IV"
author: "Tim Hendriks"
format: html
editor: visual
---

## My Meta-Analysis

My Meta-Analysis is about the effect of aerobic exercise on depression outcomes. The analysis consisted of 11 studies, of which 2 could be used for 2 outcomes, so that results in 13 effect sizes. It's called:

Morres, I. D., Hatzigeorgiadis, A., Stathi, A., Comoutos, N., Arpin-Cribbie, C., Krommidas, C., & Theodorakis, Y. (2019). Aerobic exercise for adult patients with major depressive disorder in mental health services: A systematic review and meta-analysis. Depression and Anxiety, 36(1), 39–53. <https://doi.org/10.1002/da.22842>

They report all the necessary data quite neatly, with a table with effect size per study, SE's, CI's, z-value and p-value provided. So I could conveniently copy these values into an excel file. I also chose the way their depression was measured as moderator; clinically rated vs self-rated.

## Code

```{r}
install.packages("meta")
library(readxl)
library(meta)
data <- read_excel("C:\Users\20224078\OneDrive - TU Eindhoven\Meta-Analysis-Excel.xlsx")

```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
