---
title: "Main Analysis"
author: "Tim Hendriks"
date: "2026-09-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My Meta-Analysis is about the effect of aerobic exercise on depression outcomes. The analysis consisted of 11 studies, of which 2 could be used for 2 outcomes, so that results in 13 effect sizes. It's called: 

Morres, I. D., Hatzigeorgiadis, A., Stathi, A., Comoutos, N., Arpin-Cribbie, C., Krommidas, C., & Theodorakis, Y. (2019). Aerobic exercise for adult patients with major depressive disorder in mental health services: A systematic review and meta-analysis. Depression and Anxiety, 36(1), 39–53. https://doi.org/10.1002/da.22842

They report all the necessary data quite neatly, with a table with effect size per study, SE's, CI's, z-value and p-value provided. So I could conveniently copy these values into an excel file. I also chose the way their depression was measured as moderator; clinically rated vs self-rated.


```{r cars}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
